\documentclass[12pt]{article}
\usepackage[top=0.8in, bottom=0.8in, right=0.8in, left=0.8in,
paperwidth=8.5in, paperheight=11in, nohead]{geometry}
\geometry{letterpaper}
\usepackage[pdftex]{graphicx}
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{hyperref}

\title{Lab structure}
\author{Lauren C. Ponisio}

\begin{document}
\maketitle

\section{Lab meetings/journal club}
\begin{enumerate}
\item weekly lab meetings
\item topics ranging from professional development, academic
  survivorship, current projects, relevant literature, reproducible
  science and analytic tools
% \item we being each lab meeting with a check in: ``how are you doing
%  academically? How are you doing as a person?''
\end{enumerate}

\section{Pair coding-writing meetings}
\begin{enumerate}
\item each student/post-doc meets with Lauren for 30 minutes a week,
  in addtion, a person can sign up for a 2 hr longer meeting.
\item possible meeting uses:
  \begin{enumerate}
  \item side-by-side code together, working through analyses or bugs
    in models
  \item live edit/writing
  \item refine a conceptual framework
  \item discuss professional development goals
  \item outline the framing of an article
  \end{enumerate}
\end{enumerate}

\section{Project meetings}
\begin{enumerate}
\item Thematic groups based on ongoing projects will also meet once a
  $\sim$ quarter.
\end{enumerate}

\section{Submitting grants}
\begin{enumerate}
\item as per UO policy, Lauren is a PI on all grants originating from
  the lab
\item all grants must be approved by the sponsored programs
  office. They need 3 business days before the grant is due to
  approve the grant. Submit the final grant documents only!
\item We have an assigned grant officer (Sara).  Address all questions
  regarding budgets (i.e., the graduate student step system for
  stipends) to her. Start working on budget one month prior to grant
  submission.
\end{enumerate}

\section{Requesting comments}
\begin{enumerate}
\item For manuscripts, be sure to storyboard the manuscript with
  Lauren before any serious writing.
\item Have a peer (i.e., post-doc or graduate student in the lab or
  with similar research interests) read the draft before submitting it
  to LP.
\item Add your article to the review queque in dropbox. Expect review
  to take two weeks or more depending on how many manuscripts are in
  the queue.
\item Lab members are required to write manuscripts in Latex.
\end{enumerate}

\section{Submitting manuscripts}
\begin{enumerate}
\item All coauthors must read and sign off on a manuscript before
  submission. Online submission is done by the first author.
\item before submission, re run all code, check reported statistics in
  manuscript
\item posting code and data (a subset if necessary) is a lab
  requirement
\item check references, and make sure journal names are abbreviated
\item when responding to reviews, send out revisions and latex diff
  file to all authors and give them a time line to comment, and only
  after all have responded (either with comments or by confirming they
  don't have comments) re-submit.
\end{enumerate}


\section{Requesting letters of recommendation}
Add the letter you need to lab review and letter queue in dropbox.
Include the date it is due, and detailed instructions on how it
needs to be submitted (the email, the link, etc.) to the
spreadsheet. Letters must be requested \textbf{one month in advance}
for new letters, one week for existing letters.
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-PDF-mode: t
%%% End:


