\documentclass[12pt]{article}
\usepackage[top=0.8in, bottom=0.8in, right=0.8in, left=0.8in,
paperwidth=8.5in, paperheight=11in, nohead]{geometry}
\geometry{letterpaper}
\usepackage[pdftex]{graphicx}
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{hyperref}

\title{Lab structure}
\author{Lauren C. Ponisio}

\begin{document}
\maketitle

\section{Buying things}
\begin{enumerate}
\item all purchases much go through ebuy. Do the trainings and become
  a subrequestor and order that you need (only PI and postdocs are
  requestors)
\end{enumerate}

\section{Travel}
\begin{enumerate}
\item use \href{https://www.ucgo.org/register-travel-connexus}
  {Connexus} for travel that way Ashley (Ashley Hix
  <ashley.hix@ucr.edu>) can make sure you are doing it right and you
  don't have to pay out of pocket for flights. Tips:
  \begin{enumerate}
  \item it takes a while to get access, ask early. If you don't get
    it worked out in time, have someone with access book a guest
    ticket for you
  \item it clears all reservations at midnight unless Ashley approves
    them, so book during buisness hours
  \item rental cars cannot be booked on an FAU, you have to pay out
    of pocket and be reimbused. Contracts use UC rates and insurnace
    so yours is not primary. Never book a rental car without using
    the UC rate.
  \item you can use a personal car ($0.55$ a mile), but you need to
    prove it is cheaper than flying (or a reason for why you cannot
    fly)
  \item the lab car can be used and the fuel car is linked to an
    FAU. Ask LP for approval for using the lab car.
  \item if you leave for any airport than ONT, you need to provide a
    screen shot from connexus that the other option is cheaper.
  \end{enumerate}      
\end{enumerate}

\section{Avoiding paying out of pockets}
\begin{enumerate}
\item use ebay. You must use ebuy anyways. 
\item use connexus for flights and book directly on an FAU
\item apply for a travel card. For multi-year people only. Expect it
  to take a month to receive.
\item ask for a travel fund forwarding at least 30 days in
  advance. This is a lot of work for everyone and should only be
  used in emergencies. 
\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-PDF-mode: t
%%% End:


