\documentclass[12pt]{article}
\usepackage[top=0.8in, bottom=0.8in, right=0.8in, left=0.8in,
paperwidth=8.5in, paperheight=11in, nohead]{geometry}
\geometry{letterpaper}
\usepackage[pdftex]{graphicx}
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{color}
\usepackage{titlesec}
\usepackage{fancyhdr}


\begin{document}

\section{Different parts of the interview}
\subsection{Group interviews}
\begin{itemize}
\item focus on presenting the knowledge that you have
\end{itemize}

\subsection{One-on-one}
\begin{itemize}
\item establish a report as quickly as possible
\item deep dive for information
\item prepare questions specific to the faculty member
\end{itemize}

\subsection{The dean/department chair}
\begin{itemize}
\item what is the big picture of the department/college?
\item what is the university's direction?
\item what are the major challenges?
\end{itemize}

\subsection{Dinner interviews}
\begin{itemize}
\item try to engage people, especially people who have not said much
\item practice your elevator version of what you do! Concise but
  engaging, umbrella big picture
\end{itemize}

\subsection{Graduate student meeting}
\begin{itemize}
\item Find out what they want in a candidate. What graduate courses do
  they wish were taught?
\item Engage with them! Ask a question about their research after they
  introduce themselves
\end{itemize}

\subsection{The job talk}
\begin{itemize}
\item Prepare your seminar in advance and solicit feedback from
  several sources.
\item Have a coherent story throughout, 1-3 sub-stories.
\item Contextualize your work so that people understand why it's
  important, but show you have some depth
\end{itemize}

\subsection{The chalk talk}
\begin{itemize}
\item Outline a conceptual framework for your lab. What are the big
  questions you lab will address? How to specific projects address
  these questions?
\item What is your plan in the next 1-3 years? 3-7? Big post tenure
  plans?
\item What classes would you teach? (provide example syllabi?)
\item What grants will you apply to?
\item What will your students work on?
\end{itemize}

\section{Questions to really know}
\subsection{So, what is it that you do?}
\subsection{What are your weaknesses?}
\begin{itemize}
\item cover something obvious
\item immediately talk about what you have done to mitigate it
\item give only one
\end{itemize}

\subsection{What are you strengths?}
\begin{itemize}
\item I am proud that I have accomplished...
\end{itemize}

\subsection{What is your experience...}
\begin{itemize}
\item Setting up a research program
\item collaborating with others
\item map out how you would start a lab, both big and small
\end{itemize}

\section{After the interview}
\begin{itemize}
\item send a thank you note to search committee and the people you
  connected with. Note down something during the interview you can
  mention?
\end{itemize}

\section{Misc.}
\begin{itemize}
\item Look at example start ups and think about what you might
  need. Think about things/personnel you need not just money.
\item Don't say negative things about colleagues/your old department etc.
\item Don't ask any question that assumes that you are getting the
  job.
\item Don't imply you would rather take a job somewhere else 
\end{itemize}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-PDF-mode: t
%%% End:


