\documentclass[12pt]{article}
\usepackage[top=0.8in, bottom=0.8in, right=0.8in, left=0.8in,
paperwidth=8.5in, paperheight=11in, nohead]{geometry}
\geometry{letterpaper}
\usepackage[pdftex]{graphicx}
\usepackage{color}
\usepackage[normalem]{ulem}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{setspace}
\usepackage{mdwlist}
\usepackage{hyperref}
\usepackage{xr}

\title{Expectations}
\author{Lauren C. Ponisio}

\begin{document}

\maketitle

\section{Authorship}
There are five key parts of a study:
\begin{enumerate}
\item Idea generation: Contributed to formulating the research
  question or methodology (ex., attending lab/group meetings and
  giving feedback on ideas).
\item Funding (ex., assisting on grants, giving feedback on grant ideas)
\item Data collection (including cleaning and curation): Played a
  substantial role in collecting and processing the data beyond
  routine work.
\item Analysis and Interpretation of Results: Assisted in analyzing
  and interpreting findings and providing critical insights (i.e.,
  helping to write the code to conduct the statistical analyses). 
\item Writing \& Revising Manuscript: Drafted portions of the paper or
  made substantial edits beyond proofreading.
\end{enumerate}

A good rule of thumb is a coauthor must be involved in at least three
of the five pieces. It is widely acknowledged that underrepresented
groups in science are coauthored less because their contributions are
not as easily valued or apparent. Lab members are encouraged to keep
this in mind when considering the contributions of others, and also
when advocating for their own contributions. 

We are part of community and should freely help each other whenever
appropriate, i.e., bounce ideas off each other, ask for help with
code, ran a statistical analysis by someone. That being said, it is
important to discuss coauthorship early and often. Be upfront about:

\begin{enumerate}
\item Your interest in a project
\item What you can contribute ``freely'' (i.e., without coauthorship)
\item What level of involvement you believe warrants coauthorship
  (i.e., I am happy to brain storm an analysis with you, but if I am
  developing code with you I would like to be more fully involved in
  the project and be coauthored). 
\end{enumerate}

If a person only performed routine tasks (e.g., data entry, standard
lab procedures) without intellectual input, they should instead be
acknowledged in the paper but not listed as an author.

\subsection{Undergrad and technician coauthorship}

Authorship for undergrands and technicians can be helpful to their
careers, but the came criteria apply. Best practices include:

\begin{enumerate}
\item Early and Transparent Discussion: Set Expectations: Discuss
  authorship criteria with undergrad research assistants (URAs) and
  techs early in the research process so they understand what is
  needed to qualify.
\item Mentorship \& Inclusion: Encourage URAs and techs to engage in
  higher-level thinking and analysis to give them opportunities for
  authorship.
\item Acknowledgment vs.\ Authorship: If a URA made minor contributions
  (e.g., performing lab/field work under supervision without
  independent intellectual contributions), they should be acknowledged
  rather than listed as an author. If their role grew over time and
  they contributed substantially to intellectual aspects, they should
  be considered for authorship.
\item Consensus Among Co-authors: Final decisions should be made
  collaboratively among all co-authors and supervisors to ensure
  fairness and adherence to ethical guidelines.
\end{enumerate}


\section{Reproducibility}
We are committed to using the best practices in scientific computing
and reproducible science. All the
materials needed to reproduce the study entirely (from data collection
to analysis), must be make available publicly and associated with all
publications. This includes:
\begin{enumerate}
\item Curating all data in a relational database where automated
  data cleaning is conducted that is version controlled, including a
  record of any changes to the data and the raw data is never altered.
\item Version controlling and posting all protocols (collection,
  molecular, etc.) publicly, and associate each protocol DOI with its
  corresponding publication.
\item Version control all analytic code. Final products will be
  executable from a single script with an explanatory Rmarkdown file,
  publicly available and associated with corresponding publication.
\item Post all final data publicly.
\end{enumerate}

\section{Data management}
All lab members are responsible for the curation of the data they
collect. The lab's data management protocol is:

\begin{enumerate}
\item Data will first be entered from field sheets into a spreadsheet
  on google drive or dropbox. All data must be stored in the cloud
  (shared with the PI) and not on a personal computer.
\item We will use R (or programming language of your choice) to check
  each datasets fields for consistency and typographic errors and
  output the cleaned data files for analyses. Once the raw data is entered
  it is downloaded as a \.csv file, and cleaned and
  assembled using R protocols, while never transforming the original
  Google spreadsheet. All code for cleaning data will be version
  controlled on Github so there is a record of any changes made to the
  data.
\item Data will be posted along will accompanying code for all
  publications.
\item If a lab member has left the lab/is not making progress on a
  lab-funded project for 3 months, the ownership of the data returns
  to the lab. All thesis chapter(s) must be submitted for publication
  before graduating.
\end{enumerate}

\section{Science communication}
All lab members will strive to communicate their research to a non academic
audience at least once a year (i.e., blog for National Geographic,
presentation at the Entomology fair, presentation to a school group
etc.).




\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-PDF-mode: t
%%% End:


